\section{Introduction and Related Work}

Cacophony delivers data from occasionally observable sensors.  Where sensors is
interpretted broadly to include any source of information of context
information.

Cacoph

If you consider sensors as delivering samples of the real world over time and
then send those samples through a network, the samples can be conceptualized as
a flow.to 


The idea of using data flows as perspective from which to manage contextual data
is heavily influenced by work in streaming databases and introduced to the
UbiComp community through the liquid system developed by Heer
et.al.~\cite{HeerNBH03}.  Liquid was a broad conceptual approach to context
aware data delivery that was inspired by work in streaming databases.  The
primary goal of liquid was to create links between nodes which incrementally
gathered, processed and delivered information to interested parties.

Cacophony is similar in that it also provides an architecture for connecting
computation nodes that deliver data from a source through a series of
transformations and aggregations to a sink node.

The main architectural difference between liquid and Cacophony is that liquid
made the assumption that the underlying data was continuously available.
Cacophony in contrast assumes that the underlying data is hidden and only
occassionally is an observation made that provides information about the hidden
variable of interest.  Cacophony assumes that the observations are noisy and not
always available.

Liquid also focussed on data discovery and alerting mechanisms.  Both of these
aspects of data aggregation are important, but are secondary to Cacophony's goal
of revealing hidden, occasionaly observable data.  Data discovery and alerting
mechanisms are both services that can be built on top of Cacophony and are not
central to it's focus on aggregation and statistical interpretation. 

Liquid and cacophony both take the perspective that context information is
maintained in a distributed fashion across multiple physical and organizational
boundaries.

Liquid makes some claims about it's ability to reroute queries in order to
follow mobile entities.  Cacophony does not attempt to reroute its data flows
beyond the mechanisms supported by the underlying networking protocols.  Once a
source of data is provided to Cacophony, Cacophony assumes that the data is
available at that location for all time.

In contrast, cacophony does provide robust mechanisms for rapid duplication of
streams.  

Another way of looking at cacophony is not as a competitor to liquid, but as a
wrapper for liquid. 

If liquid performs distributed "queries", Cacophony performs distributed
statistically learning of context.  Liquid's primary focus is data discovery,
cacophony is about robust prediction of context.

Cacophony is not really an architecture for "streaming data" as much as
"streaming computation" which is presenting interpretations of instantaneous
data.

liquid encodes the idea of entities.  Cacophony supports entity prediction, but
doesn not expect a particular semantic on the underlying data.



Is there prior work before liquid?

What has come after liquid?  Does it relate?
\cite{Hong2004}

